### 2017-02-02 mu/mpxerr.tex
Checking most intense responses for v^ab.

\gdef\mpxshipout{\shipout\hbox\bgroup
  \setbox0=\hbox\bgroup}
\gdef\stopmpxshipout{\egroup  \dimen0=\ht0 \advance\dimen0\dp0
  \dimen1=\ht0 \dimen2=\dp0
  \setbox0=\hbox\bgroup
    \box0
    \ifnum\dimen0>0 \vrule width1sp height\dimen1 depth\dimen2 
    \else \vrule width1sp height1sp depth0sp\relax
    \fi\egroup
  \ht0=0pt \dp0=0pt \box0 \egroup}
\mpxshipout% line 125 ./up-Dxb.mp
-500000%
\stopmpxshipout
\mpxshipout% line 128 ./up-Dxb.mp
-400000%
\stopmpxshipout
\mpxshipout% line 131 ./up-Dxb.mp
-300000%
\stopmpxshipout
\mpxshipout% line 134 ./up-Dxb.mp
-200000%
\stopmpxshipout
\mpxshipout% line 137 ./up-Dxb.mp
-100000%
\stopmpxshipout
\mpxshipout% line 140 ./up-Dxb.mp
0%
\stopmpxshipout
\mpxshipout% line 143 ./up-Dxb.mp
100000%
\stopmpxshipout
\mpxshipout% line 146 ./up-Dxb.mp
200000%
\stopmpxshipout
\mpxshipout% line 149 ./up-Dxb.mp
300000%
\stopmpxshipout
\mpxshipout% line 152 ./up-Dxb.mp
400000%
\stopmpxshipout
\mpxshipout% line 155 ./up-Dxb.mp
500000%
\stopmpxshipout
\mpxshipout% line 159 ./up-Dxb.mp
0%
\stopmpxshipout
\mpxshipout% line 163 ./up-Dxb.mp
0.2%
\stopmpxshipout
\mpxshipout% line 167 ./up-Dxb.mp
0.4%
\stopmpxshipout
\mpxshipout% line 171 ./up-Dxb.mp
0.6%
\stopmpxshipout
\mpxshipout% line 175 ./up-Dxb.mp
0.8%
\stopmpxshipout
\mpxshipout% line 179 ./up-Dxb.mp
1%
\stopmpxshipout
\mpxshipout% line 183 ./up-Dxb.mp
1.2%
\stopmpxshipout
\mpxshipout% line 187 ./up-Dxb.mp
C$_{16}$H$_{8}$-up%
\stopmpxshipout
\mpxshipout% line 189 ./up-Dxb.mp
\Large $\mu^{abcd}(\,J\,s^{-1}\,V^{-2})$%
\stopmpxshipout
\mpxshipout% line 191 ./up-Dxb.mp
{\Large Photon Energy (eV)}%
\stopmpxshipout
\mpxshipout% line 194 ./up-Dxb.mp
D^{xx}%
\stopmpxshipout
% line 262 ./up-Dxb.mp
 \end{document}

>>>>

\gdef\mpxshipout{\shipout\hbox\bgroup
  \setbox0=\hbox\bgroup}
\gdef\stopmpxshipout{\egroup  \dimen0=\ht0 \advance\dimen0\dp0
  \dimen1=\ht0 \dimen2=\dp0
  \setbox0=\hbox\bgroup
    \box0
    \ifnum\dimen0>0 \vrule width1sp height\dimen1 depth\dimen2 
    \else \vrule width1sp height1sp depth0sp\relax
    \fi\egroup
  \ht0=0pt \dp0=0pt \box0 \egroup}
\mpxshipout% line 125 ./intense-responses-mu-all.mp
-2e-06%
\stopmpxshipout
\mpxshipout% line 128 ./intense-responses-mu-all.mp
-1.8e-06%
\stopmpxshipout
\mpxshipout% line 131 ./intense-responses-mu-all.mp
-1.6e-06%
\stopmpxshipout
\mpxshipout% line 134 ./intense-responses-mu-all.mp
-1.4e-06%
\stopmpxshipout
\mpxshipout% line 137 ./intense-responses-mu-all.mp
-1.2e-06%
\stopmpxshipout
\mpxshipout% line 140 ./intense-responses-mu-all.mp
-1e-06%
\stopmpxshipout
\mpxshipout% line 143 ./intense-responses-mu-all.mp
-8e-07%
\stopmpxshipout
\mpxshipout% line 146 ./intense-responses-mu-all.mp
-6e-07%
\stopmpxshipout
\mpxshipout% line 149 ./intense-responses-mu-all.mp
-4e-07%
\stopmpxshipout
\mpxshipout% line 152 ./intense-responses-mu-all.mp
-2e-07%
\stopmpxshipout
\mpxshipout% line 155 ./intense-responses-mu-all.mp
0%
\stopmpxshipout
\mpxshipout% line 158 ./intense-responses-mu-all.mp
2e-07%
\stopmpxshipout
\mpxshipout% line 162 ./intense-responses-mu-all.mp
0%
\stopmpxshipout
\mpxshipout% line 166 ./intense-responses-mu-all.mp
0.5%
\stopmpxshipout
\mpxshipout% line 170 ./intense-responses-mu-all.mp
1%
\stopmpxshipout
\mpxshipout% line 174 ./intense-responses-mu-all.mp
1.5%
\stopmpxshipout
\mpxshipout% line 178 ./intense-responses-mu-all.mp
2%
\stopmpxshipout
\mpxshipout% line 182 ./intense-responses-mu-all.mp
2.5%
\stopmpxshipout
\mpxshipout% line 186 ./intense-responses-mu-all.mp
3%
\stopmpxshipout
\mpxshipout% line 191 ./intense-responses-mu-all.mp
{\Large Photon Energy (eV)}%
\stopmpxshipout
\mpxshipout% line 194 ./intense-responses-mu-all.mp
cdse zzzz%
\stopmpxshipout
\mpxshipout% line 501 ./intense-responses-mu-all.mp
gaas xxxxhnbGh-aa/hnbGh-aa-res-0-4-2001pts/mu.sm_0.03_xyxx_xyxy_xyxz_xyyx_xyyy_xyyz_xyzx_xyzy_xyzz_14452_75-spin_scissor_0_Nc_32%
\stopmpxshipout
% line 814 ./intense-responses-mu-all.mp
 \end{document}
